Analysis of the 2014 Passenger Flight Network

### 2020-02-19 paper/main.tex

\begin{abstract}
In this case study we are looking at a dataset about air travel in 2014. 
We implement some mechanisms to clean the data, as well as mechanisms to enrich this dataset with information we query from wikidata.
We estimate some missing data.
Starting from there, we analyze some network characteristics for the whole network as well as airline-specific sub-networks.
We compare airline-specific networks and find relations between their network's characteristics and their business model.
We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
We compare it's predictive correctness to the real world. 
We criticise the proposed metric and present a different approach. 
\end{abstract}

@@

\begin{figure}[h]

	\centering
	\includegraphics[width=76mm]{imgs/results/ego_graph_730.png}
	\caption{Worst situation in the scenario, where patronage is based on neighboring airport's patronage: 
Arvidsjaur Airport is only connected to Lycksele Airport but has a more than twice as high patronage than Lycksele Airport}
	\label{fig:worst_flow_fit}
\end{figure}

@@

\begin{table}[ht]
\begin{center}
 \begin{tabular}{| l | r | r | r |}
 \hline
 \textbf{Airline} & \textbf{Mean} & \textbf{Median} & \textbf{Diam.} \\ 
 \hline
 United & 2353.69 & 1393 & 12979 \\
 \hline   
 American & 2321.23 & 1371 & 14076 \\
 \hline   
 Delta & 2352.17 & 1341 & 13581 \\
 \hline   
 Ryan Air & 1490.21 & 1435 & 3698 \\
 \hline   
 Southwest & 1398.37 & 1267 & 3757 \\
 \hline   
 Air Asia & 1328.57 & 1254 & 2914 \\
 \hline   
 Ch. Southern & 1459.95 & 1127 & 11637 \\
 \hline   
 Ch. Eastern & 1427.81 & 1075 & 11896 \\
 \hline
 \end{tabular}
\caption{Mean, median and diameter of subgraphs of major airlines (all numbers in km)}
\label{Tab:distance_airlines}
\end{center}
\end{table}

\begin{table}[ht]
\begin{center}
 \begin{tabular}{| l | r | r |}
 \hline
 \textbf{Airline} & \textbf{Mean Flow} & \textbf{Median Flow} \\ 
 \hline
 United & 85159 & 43286 \\
 \hline
 American & 67983.40 & 47185 \\
 \hline
 Delta & 76345.95  & 47123 \\
 \hline
 Ryan Air & 31268.60 & 26857.50 \\
 \hline
 Southwest & 65692.70  & 61590 \\
 \hline
 Ch. Southern & 53100  & 43729.50 \\
 \hline
 Ch. Eastern & 52610.60  & 43294 \\
 \hline
 \end{tabular}
\caption{Passenger flow of major airlines}
\label{Tab:passenger_flow_airlines}
\end{center}
\end{table}

@@

We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}. An remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (the green alliance) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand. It also does not operate much in Canada in both the generated and real alliances landscape. 
As expected, there are also differences: For example the generated alliance Landscape suggests Spanish speaking South American Countries to be in the same alliance and have Brazilian operators that are mostly part of the green alliance, while in real life Buenos Aires is tied to the Skyteam while Brazil gets supplied by a mix of alliances. Japan for example belongs to Staralliance in the real world while in the generated landscape it's a part of the green alliance.

\begin{figure}
	\centering
	\includegraphics[width=76mm]{imgs/generated-alliance-map.png}
	\caption{
The generated alliance landscape. Different colors mean different alliances. Green, Blue, Purple, Yellow. (Be aware, that by layering the networks of the different alliances on top of each other and routes in a higher layer covering the lower levels, the perception might be distorted.)}
	\label{fig:generated-alliance-map}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=76mm]{imgs/real-alliance-map.png}
	\caption{
The real alliance landscape. Skyteam(green), Staralliance(blue), Oneworld(purple), Vanilla(yellow)}
	\label{fig:real-alliance-map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=80mm]{imgs2/results/patronage_eigenvector.png}
	\caption{
	Patronage vs Eigenvector Distribution}
\label{fig:patronage_eigenvector}
\end{figure}

@@

\section*{Acknowledgments}
We thank our professor Prof. Ph.D. Ikonnikova and Sofia Berdysheva for their brilliance, support and for giving this outstanding course at TUM.

\bibliographystyle{IEEEtran}
\bibliography{literature}

>>>>

\begin{abstract}
In this case study we are looking at a dataset about air travel in 2014. 
We implement some mechanisms to clean the data, as well as mechanisms to enrich this dataset with information we query from wikidata.
We estimate some missing data.
Starting from there, we analyze some network characteristics for the whole network as well as airline-specific sub-networks.
We compare airline-specific networks and find relations between their network's characteristics and their business model.
We propose one metric that plays a role in forecasting whether a cooperation between two airlines is advantageous and use this metric to generate an alliances landscape.
We compare it's predictive correctness to the real world, criticise it and present one promising further approach. 
\end{abstract}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=76mm]{imgs/results/ego_graph_730.png}
	\caption{Worst situation in the scenario, where patronage is based on neighboring airport's patronage: 
Arvidsjaur Airport is only connected to Lycksele Airport but has a more than twice as high patronage than Lycksele Airport}
	\label{fig:worst_flow_fit}
\end{figure}

@@

\begin{table}[h]
\begin{center}
 \begin{tabular}{| l | r | r | r |}
 \hline
 \textbf{Airline} & \textbf{Mean} & \textbf{Median} & \textbf{Diam.} \\ 
 \hline
 United & 2353.69 & 1393 & 12979 \\
 \hline   
 American & 2321.23 & 1371 & 14076 \\
 \hline   
 Delta & 2352.17 & 1341 & 13581 \\
 \hline   
 Ryan Air & 1490.21 & 1435 & 3698 \\
 \hline   
 Southwest & 1398.37 & 1267 & 3757 \\
 \hline   
 Air Asia & 1328.57 & 1254 & 2914 \\
 \hline   
 Ch. Southern & 1459.95 & 1127 & 11637 \\
 \hline   
 Ch. Eastern & 1427.81 & 1075 & 11896 \\
 \hline
 \end{tabular}
\caption{Mean, median and diameter of subgraphs of major airlines (all numbers in km)}
\label{Tab:distance_airlines}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
 \begin{tabular}{| l | r | r |}
 \hline
 \textbf{Airline} & \textbf{Mean Flow} & \textbf{Median Flow} \\ 
 \hline
 United & 85159 & 43286 \\
 \hline
 American & 67983.40 & 47185 \\
 \hline
 Delta & 76345.95  & 47123 \\
 \hline
 Ryan Air & 31268.60 & 26857.50 \\
 \hline
 Southwest & 65692.70  & 61590 \\
 \hline
 Ch. Southern & 53100  & 43729.50 \\
 \hline
 Ch. Eastern & 52610.60  & 43294 \\
 \hline
 \end{tabular}
\caption{Passenger flow of major airlines}
\label{Tab:passenger_flow_airlines}
\end{center}
\end{table}

@@

We plot the result on a world map (Figure~\ref{fig:generated-alliance-map}) and compare it to the real alliance landscape (Figure~\ref{fig:real-alliance-map}. A remarkable similarity between the generated alliance landscape and the real one, is that one big alliance (the green alliance) is covering a lot of flights between the US, Europe and China, but is not much active in South America, South Africa, Australia or New Zealand. It also does not operate much in Canada in both the generated and real alliances landscape. 
As expected, there are also differences: For example the generated alliance Landscape suggests Spanish speaking South American Countries to be in the same alliance and have Brazilian operators that are mostly part of the green alliance, while in real life Buenos Aires is tied to the Skyteam while Brazil gets supplied by a mix of alliances. Japan for example belongs to Staralliance in the real world while in the generated landscape it's a part of the green alliance.

\begin{figure}[t]
	\centering
	\includegraphics[width=76mm]{imgs/generated-alliance-map.png}
	\caption{
The generated alliance landscape. Different colors mean different alliances. Green, Blue, Purple, Yellow. (Be aware, that by layering the networks of the different alliances on top of each other and routes in a higher layer covering the lower levels, the perception might be distorted.)}
	\label{fig:generated-alliance-map}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=76mm]{imgs/real-alliance-map.png}
	\caption{
The real alliance landscape. Skyteam(green), Staralliance(blue), Oneworld(purple), Vanilla(yellow)}
	\label{fig:real-alliance-map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=80mm]{imgs2/results/patronage_eigenvector.png}
	\caption{
	Patronage vs. eigenvector distribution}
\label{fig:patronage_eigenvector}
\end{figure}

@@

\section*{Acknowledgments}
We thank Prof. Ikonnikova and Sofia Berdysheva for their inspiration, support and for giving this outstanding course at TUM. 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\bibliographystyle{IEEEtran}
\bibliography{literature}
